\cvsection{Experience}

\begin{cventries}

  \cventry
  {Principal Systems Architect}
  {Divergent Tabletop}
  {Cape Town}
  {Jul 2025 -- Present}
  {
    \begin{cvitems}
      \item Engineered and hosted an enterprise-grade documentation ecosystem
      \item Implemented a single-database multi-tenant separation engine using PostgreSQL Row-Level Security (RLS) and transaction-scoped local parameters (\texttt{SET LOCAL}), enforcing strict data silos across isolated groups.
      \item Designed an atomic asynchronous flush strategy using in-memory GenServer storage buffers, reducing database persistent write transactions by 85\% during periods of high user interaction.
      \item Utilized \texttt{Ecto.Multi} atomic chains and \texttt{Oban} transactional background workers to ensure multi-stage backend edits (e.g., structural document renaming and incoming backlink indexing) execute completely or roll back safely.
      \item Applied Universal Design and Executive Functioning support models to product UX/UI; established highly structured, low-context asynchronous operational playbooks that minimized cognitive friction for contributors.
    \end{cvitems}
  }

  \cventry
  {Full-Stack ERPNext \& Automation Engineer}
  {FARO Africa}
  {Cape Town}
  {Aug 2024 -- Nov 2025}
  {
    \begin{cvitems}
      \item Refactored and extended ERPNext via Python and JavaScript server hooks, optimizing pricing matrices and business intelligence reporting.
      \item Architected migration of internal Retool workflows to React Native/Expo mobile ecosystem, reducing vendor licensing overhead.
      \item Built custom NFC scanner communication utilities within Expo applications for instantaneous physical inventory syncs.
      \item Provisioned AWS infrastructure with Pulumi, deploying Inngest event-driven functions and PayloadCMS.
      \item Diagnosed and resolved issues in a large existing ERPNext installation; introduced LLM-assisted debugging workflows.
    \end{cvitems}
  }

  \cventry
  {Enterprise Infrastructure \& Tooling Engineer}
  {Ingenics Digital GmbH \emph{(through ViVa Outsourcing)}}
  {Remote Work}
  {Mar 2023 -- May 2024}
  {
    \begin{cvitems}
      \item Built modular Python utility structures and automation scripts for internal configuration schema validation.
      \item Designed data handling pipelines ensuring data transfer consistency across runtime platforms using declarative specifications.
      \item Developed Python hardware mocks enabling faster development cycles with fewer hardware dependencies.
    \end{cvitems}
  }

  \cventry
  {Junior Lecturer}
  {North-West University}
  {Potchefstroom}
  {Feb 2020 -- Dec 2020}
  {
    \begin{cvitems}
      \item Lectured Python and C++ programming for Introduction to Programming for first year IT students. \\
    \end{cvitems}
  }

\end{cventries}
